SSA based global code motion of identical computations

### 2017-04-15 acmart-pacmpl-template.tex
contrib and click

The main contributions of this paper are:
\begin{itemize}
\item a new optimistic algorithm to move computations out of branches,
\item a cost model to reduce interference and reduce spills,
\item a technique to maximize hoisting in an optimistic approach by partitioning
  the list of potential candidates sorted by their DFS visit number,
\item experimental evaluation of our implementation in \LLVM{} which combines
  SSA based liveness analysis, and ranking of expressions to move very busy
  expressions in order to reduce code-size (and improve performance in some
  cases).
\end{itemize}

@@

@@

\subsection{Liveness using DJ Graph}
The DJ Graph is very useful for computing liveness because the values will only
flow either through dominator edges or the join edges (where we insert a PHI).

>>>>

There have been a lot of work both in industry and academia to hoist and sink
code out of branches, and in general global scheduling
\cite{click1995global}. Some relate code-hoisting to code-size optimization
\cite{rosen1988global} and many \cite{barany2013, shobaki2013} use global
scheduling to improve performance. Most of the recent work on global scheduling
are done using ILP which results in prohibitively high compile time. To the best
of our knowledge we have not found any reference which explored code-motion of
identical computation in as much detail as we have done. We have also open
sourced the implementation for easy verification. The main contributions of this
paper are:
\begin{itemize}
\item a new optimistic algorithm to move computations out of branches,
\item a cost model to reduce interference and reduce spills,
\item a technique to maximize hoisting in an optimistic approach by partitioning
  the list of potential candidates sorted by their DFS visit number,
\item experimental evaluation of our implementation in \LLVM{} which combines
  SSA based liveness analysis, and ranking of expressions to move very busy
  expressions in order to reduce code-size (and improve performance in some
  cases).
\end{itemize}

@@

Click \cite{click1995global} describe aggressive global code motion to first
schedule all the instructions as early as possible. This results in very long
live ranges which is mitigated by again scheduling all the instructions as late
as possible. They report sppeedup of as high as $23\%$.

@@

\subsection{Liveness using DJ Graph}
DJ-Graph \cite{Sreedhar1996} is a data structure that augments the dominator
tree with join-edges to keep track of data-flow in a program. We use DJ-Graph to
compute liveness of variables as illustrated in \cite{das2012}.  It is very
efficient for computing liveness because the values will only flow either
through dominator edges or the join edges (where we insert a PHI).
